---
title: "correlation_variable_pc_051519"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#want to see the correlation between variables and three first pcs, I used this link to get corr between categorical and continuous variables "https://rpubs.com/juanhklopper/biserial_correlation"

#For a dichotomous categorical variable and a continuous variable you can calculate a Pearson correlation if the categorical variable has a 0/1-coding for the categories. This correlation is then also known as a point-biserial correlation coefficient. But when you have more than two categories for the categorical variable the Pearson correlation is not appropriate anymore. You should then use eta-squared, or eta, as an effect-size measure for the relationship of a categorical variable and a continuous variable. 
```{r}
load("../Input_Output/RData/merge_final.RData")
SNP_PC1_PC2_PC3_Plink_v2 <- read.delim("C:/eQTL/R_eQTL_Stroke/Input_Output/SNP_PC1_PC2_PC3_Plink_v2.txt", row.names=1)
#install.packages("polycor")
#library("polycor")
polyserial(merge_v3$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2) # check for sex, historyhypertension, historydiabetesmellitus and  historyhypercholestrolemi, the sum r for these three pcs with these variables are more than 15%
merge_v3_categorical_variables <- merge_v3[,c(292999,293000,293002,293003,293004,293005)] #categorical variables
cor <- polyserial(merge_v3_categorical_variables$sex,SNP_PC1_PC2_PC3_Plink_v2$PC1) # -0.1028759
cor <- polyserial(merge_v3_categorical_variables$sex,SNP_PC1_PC2_PC3_Plink_v2$PC2) #-0.02800927
cor <- polyserial(merge_v3_categorical_variables$sex,SNP_PC1_PC2_PC3_Plink_v2$PC3) # -0.06754498
#0.10*100+0.02*100+0.06*100=18
cor <- polyserial(merge_v3_categorical_variables$historyhypertension,SNP_PC1_PC2_PC3_Plink_v2$PC1) # 0.08958846
cor <- polyserial(merge_v3_categorical_variables$historyhypertension,SNP_PC1_PC2_PC3_Plink_v2$PC2) # -0.03533174
cor <- polyserial(merge_v3_categorical_variables$historyhypertension,SNP_PC1_PC2_PC3_Plink_v2$PC3) # 0.0854686
#0.08958846*100+0.03533174*100+0.0854686*100= 21
cor <- polyserial(merge_v3_categorical_variables$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2$PC1) # 0.1225268
cor <- polyserial(merge_v3_categorical_variables$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2$PC2) # -0.03719701
cor <- polyserial(merge_v3_categorical_variables$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2$PC3) # -0.002408439
#0.1225268*100+0.03719701*100+0.002408439*100 = 16.21322
cor <- polyserial(merge_v3_categorical_variables$historyhypercholestrolemia,SNP_PC1_PC2_PC3_Plink_v2$PC1) # -0.06071567
cor <- polyserial(merge_v3_categorical_variables$historyhypercholestrolemia,SNP_PC1_PC2_PC3_Plink_v2$PC2) # 0.02673601
cor <- polyserial(merge_v3_categorical_variables$historyhypercholestrolemia,SNP_PC1_PC2_PC3_Plink_v2$PC3) # 0.09137698
#0.06071567*100+0.02673601*100+0.09137698*100=17.88
```

```{r}
merge_v3_categorical_variables_pcs <- cbind(merge_v3_categorical_variables,SNP_PC1_PC2_PC3_Plink_v2)
cor <-hetcor(merge_v3_categorical_variables_pcs, ML=FALSE) #pearson type of cor slightly different with biserial
cor$correlations
#                                    sex        race historyhypertension historydiabetesmellitus historyhypercholestrolemia   diagnosis
# sex                         1.00000000  0.09647878         -0.03752592             -0.07525913               -0.129120897  0.26790774
# race                        0.09647878  1.00000000         -0.08578327             -0.04880125                0.041533148  0.05177473
# historyhypertension        -0.03752592 -0.08578327          1.00000000              0.26569963                0.355658903 -0.27559299
# historydiabetesmellitus    -0.07525913 -0.04880125          0.26569963              1.00000000                0.246901909 -0.24979313
# historyhypercholestrolemia -0.12912090  0.04153315          0.35565890              0.24690191                1.000000000 -0.14744777
# diagnosis                   0.26790774  0.05177473         -0.27559299             -0.24979313               -0.147447772  1.00000000
# PC1                        -0.04344418 -0.47985991          0.10005500              0.13704772               -0.095407258 -0.06669989
# PC2                        -0.07112025 -0.25634956          0.02360019              0.02984701                0.002520536  0.02473808
# PC3                        -0.03862215 -0.48104226          0.01457055              0.01708294                0.041713235 -0.13751925
#                                      PC1           PC2           PC3
# sex                        -4.344418e-02 -7.112025e-02 -3.862215e-02
# race                       -4.798599e-01 -2.563496e-01 -4.810423e-01
# historyhypertension         1.000550e-01  2.360019e-02  1.457055e-02
# historydiabetesmellitus     1.370477e-01  2.984701e-02  1.708294e-02
# historyhypercholestrolemia -9.540726e-02  2.520536e-03  4.171323e-02
# diagnosis                  -6.669989e-02  2.473808e-02 -1.375192e-01
# PC1                         1.000000e+00 -2.158432e-08 -4.162922e-08
# PC2                        -2.158432e-08  1.000000e+00  5.524897e-08
# PC3                        -4.162922e-08  5.524897e-08  1.000000e+00
```

```{r}
heatmap(cor$correlations)
#library("reshape2")
melt<-melt(cor$correlations)
#library("ggplot2")
G=ggplot(melt)
G+geom_tile(aes(Var2,Var1,fill=value))
rcm=round(cor$correlations,2) #Fancier with ggplot2
meltrcm=melt(rcm)
G=ggplot(meltrcm)
G+geom_tile(aes(Var2,Var1,fill=value))+geom_text(aes(Var2,Var1,label=value))
```


