---
title: "correlation_variable_pc_051519"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#want to see the correlation between variables and three first pcs, I used this link to get corr between categorical and continuous variables "https://rpubs.com/juanhklopper/biserial_correlation"

#For a dichotomous categorical variable and a continuous variable you can calculate a Pearson correlation if the categorical variable has a 0/1-coding for the categories. This correlation is then also known as a point-biserial correlation coefficient. But when you have more than two categories for the categorical variable the Pearson correlation is not appropriate anymore. You should then use eta-squared, or eta, as an effect-size measure for the relationship of a categorical variable and a continuous variable. 

```{r}
load("../Input_Output/RData/merge_final.RData")
SNP_PC1_PC2_PC3_Plink_v2 <- read.delim("C:/eQTL/R_eQTL_Stroke/Input_Output/SNP_PC1_PC2_PC3_Plink_v2.txt", row.names=1)
#install.packages("polycor")
#library("polycor")
polyserial(merge_v3$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2) # check for sex, historyhypertension, historydiabetesmellitus and  historyhypercholestrolemi, the sum r for these three pcs with these variables are more than 15%
merge_v3_categorical_variables <- merge_v3[,c(292999,293000,293002,293003,293004,293005)] #categorical variables
cor <- polyserial(merge_v3_categorical_variables$sex,SNP_PC1_PC2_PC3_Plink_v2$PC1) # -0.1028759
cor <- polyserial(merge_v3_categorical_variables$sex,SNP_PC1_PC2_PC3_Plink_v2$PC2) #-0.02800927
cor <- polyserial(merge_v3_categorical_variables$sex,SNP_PC1_PC2_PC3_Plink_v2$PC3) # -0.06754498
#0.10*100+0.02*100+0.06*100=18
cor <- polyserial(merge_v3_categorical_variables$historyhypertension,SNP_PC1_PC2_PC3_Plink_v2$PC1) # 0.08958846
cor <- polyserial(merge_v3_categorical_variables$historyhypertension,SNP_PC1_PC2_PC3_Plink_v2$PC2) # -0.03533174
cor <- polyserial(merge_v3_categorical_variables$historyhypertension,SNP_PC1_PC2_PC3_Plink_v2$PC3) # 0.0854686
#0.08958846*100+0.03533174*100+0.0854686*100= 21
cor <- polyserial(merge_v3_categorical_variables$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2$PC1) # 0.1225268
cor <- polyserial(merge_v3_categorical_variables$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2$PC2) # -0.03719701
cor <- polyserial(merge_v3_categorical_variables$historydiabetesmellitus,SNP_PC1_PC2_PC3_Plink_v2$PC3) # -0.002408439
#0.1225268*100+0.03719701*100+0.002408439*100 = 16.21322
cor <- polyserial(merge_v3_categorical_variables$historyhypercholestrolemia,SNP_PC1_PC2_PC3_Plink_v2$PC1) # -0.06071567
cor <- polyserial(merge_v3_categorical_variables$historyhypercholestrolemia,SNP_PC1_PC2_PC3_Plink_v2$PC2) # 0.02673601
cor <- polyserial(merge_v3_categorical_variables$historyhypercholestrolemia,SNP_PC1_PC2_PC3_Plink_v2$PC3) # 0.09137698
#0.06071567*100+0.02673601*100+0.09137698*100=17.88
```

```{r}
merge_v3_categorical_variables_pcs <- cbind(merge_v3_categorical_variables,SNP_PC1_PC2_PC3_Plink_v2)
cor <-hetcor(merge_v3_categorical_variables_pcs, ML=FALSE) #pearson type of cor slightly different with biserial
cor$correlations
#                                    sex        race historyhypertension historydiabetesmellitus historyhypercholestrolemia   diagnosis
# sex                         1.00000000  0.09647878         -0.03752592             -0.07525913               -0.129120897  0.26790774
# race                        0.09647878  1.00000000         -0.08578327             -0.04880125                0.041533148  0.05177473
# historyhypertension        -0.03752592 -0.08578327          1.00000000              0.26569963                0.355658903 -0.27559299
# historydiabetesmellitus    -0.07525913 -0.04880125          0.26569963              1.00000000                0.246901909 -0.24979313
# historyhypercholestrolemia -0.12912090  0.04153315          0.35565890              0.24690191                1.000000000 -0.14744777
# diagnosis                   0.26790774  0.05177473         -0.27559299             -0.24979313               -0.147447772  1.00000000
# PC1                        -0.04344418 -0.47985991          0.10005500              0.13704772               -0.095407258 -0.06669989
# PC2                        -0.07112025 -0.25634956          0.02360019              0.02984701                0.002520536  0.02473808
# PC3                        -0.03862215 -0.48104226          0.01457055              0.01708294                0.041713235 -0.13751925
#                                      PC1           PC2           PC3
# sex                        -4.344418e-02 -7.112025e-02 -3.862215e-02
# race                       -4.798599e-01 -2.563496e-01 -4.810423e-01
# historyhypertension         1.000550e-01  2.360019e-02  1.457055e-02
# historydiabetesmellitus     1.370477e-01  2.984701e-02  1.708294e-02
# historyhypercholestrolemia -9.540726e-02  2.520536e-03  4.171323e-02
# diagnosis                  -6.669989e-02  2.473808e-02 -1.375192e-01
# PC1                         1.000000e+00 -2.158432e-08 -4.162922e-08
# PC2                        -2.158432e-08  1.000000e+00  5.524897e-08
# PC3                        -4.162922e-08  5.524897e-08  1.000000e+00
```


```{r}
#have cor matrix for the 275 samples for the covariates matrix
merge_v3_small <- merge_v3[,c(294126:294137)]
dim(merge_v3_small) #275 11
colnames(merge_v3_small)
cor <-hetcor(merge_v3_small, ML=FALSE)
#                            diagnosissubtype       gender        race          age historyhypertension												
# diagnosissubtype                1.000000000  0.139496260  0.08487380 -0.038008372         -0.10818514												
# gender                          0.139496260  1.000000000  0.12027648  0.160118951          0.22427005												
# race                            0.084873796  0.120276480  1.00000000 -0.077842522         -0.07830122												
# age                            -0.038008372  0.160118951 -0.07784252  1.000000000          0.25969682												
# historyhypertension            -0.108185143  0.224270049 -0.07830122  0.259696818          1.00000000												
# historydiabetesmellitus        -0.077200894  0.089499197 -0.07947389 -0.086056124          0.12825872												
# historyhypercholestrolemia     -0.003062698 -0.003742024  0.03975287  0.104851237          0.24794801												
# pc1                            -0.079706907 -0.029434515 -0.48533334 -0.159889705          0.09270059												
# pc2                            -0.004472388 -0.093231493 -0.31601957  0.042071567          0.03419468												
# pc3                             0.166481547  0.066296602  0.48488074 -0.165082595          0.03945521												
# pc4                            -0.027509796  0.110308808 -0.04550506  0.002660222          0.05096513												
# diagnosis                       0.942484544  0.121595671  0.06788684 -0.016875745         -0.09790812												
#                            historydiabetesmellitus historyhypercholestrolemia           pc1           pc2												
# diagnosissubtype                     -0.0772008943               -0.003062698 -7.970691e-02 -4.472388e-03												
# gender                                0.0894991969               -0.003742024 -2.943451e-02 -9.323149e-02												
# race                                 -0.0794738870                0.039752873 -4.853333e-01 -3.160196e-01												
# age                                  -0.0860561239                0.104851237 -1.598897e-01  4.207157e-02												
# historyhypertension                   0.1282587171                0.247948010  9.270059e-02  3.419468e-02												
# historydiabetesmellitus               1.0000000000                0.134669349  1.717686e-01 -4.144936e-04												
# historyhypercholestrolemia            0.1346693495                1.000000000 -8.931343e-02  1.289256e-02												
# pc1                                   0.1717685848               -0.089313427  1.000000e+00  6.636229e-08												
# pc2                                  -0.0004144936                0.012892563  6.636229e-08  1.000000e+00												
# pc3                                  -0.0086065098                0.001954866 -3.188667e-08 -2.221934e-08												
# pc4                                  -0.0598025189               -0.047442034 -3.828227e-07  7.953805e-09												
# diagnosis                            -0.1075758038               -0.018010402 -8.348625e-02  3.907250e-02												
#                                      pc3           pc4     											
# diagnosissubtype            1.664815e-01 -2.750980e-02  												
# gender                      6.629660e-02  1.103088e-01  												
# race                        4.848807e-01 -4.550506e-02  												
# age                        -1.650826e-01  2.660222e-03 												
# historyhypertension         3.945521e-02  5.096513e-02 												
# historydiabetesmellitus    -8.606510e-03 -5.980252e-02 												
# historyhypercholestrolemia  1.954866e-03 -4.744203e-02 												
# pc1                        -3.188667e-08 -3.828227e-07 												
# pc2                        -2.221934e-08  7.953805e-09  												
# pc3                         1.000000e+00 -8.439381e-08  												
# pc4                        -8.439381e-08  1.000000e+00  												
# diagnosis                   1.383639e-01  6.445703e-04												

```

```{r}
#have a upper and lower traingle heatmap with value
#library("reshape2")
#library("ggplot2")
G+geom_tile(aes(Var2,Var1,fill=value))
rcm=round(cor$correlations,2) #Fancier with ggplot2
meltrcm=melt(rcm)
G=ggplot(meltrcm)
G+geom_tile(aes(Var2,Var1,fill=value))+geom_text(aes(Var2,Var1,label=value))

```

```{r}
load("../../Input_Output/RData/merge_final_275.RData")
dim(merge_v3) # 275 294137
merge_v3_small <- merge_v3[,c(294126:294136)] #275 12
colnames(merge_v3_small) <- c("diagnosis subtype","sex","race","age","hypertension","diabetes","hypercholestrolemia","pc1","pc2","pc3","pc4")
cor <-hetcor(merge_v3_small, ML=FALSE)
```

```{r}
#have a upper and lower traingle heatmap with no value
#heatmap(cor$correlations)
#library("reshape2")
#library("ggplot2")
G+geom_tile(aes(Var2,Var1,fill=value))
rcm=round(cor$correlations,2) #Fancier with ggplot2
meltrcm=melt(rcm)
G=ggplot(meltrcm)
G+geom_tile(aes(Var2,Var1,fill=value))+geom_text(aes(Var2,Var1,label=value))
```



```{r}
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

```

```{r}
cormat <- round(cor(merge_v3_small),2)
cormat <- round(cor(merge_v3_small),2)^2
melted_cormat <- melt(cormat)
ggplot(data = meltrcm, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```

```{r}
get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
```

```{r}
upper_tri <- get_upper_tri(cormat)

```

```{r}
# Melt the correlation matrix (R2)
library(reshape2)
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Heatmap
library(ggplot2)
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(0,1), space = "Lab", 
   name="R2") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()
```


